---
title: "Processing Occurrence Data"
author: "Emily Bellis"
date: "8/31/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description 
This R markdown document describes cleaning of occurrence data and generation of background points for *Cuscuta* species described in Masanga *et al.* (submitted).

## Load libraries
```{r}
library(raster)
library(maps)
library(rgdal)
library(rgbif)
library(dplyr)
library(dismo)
data(worldMapEnv)
```


## Field data for Kenya collected by Runo lab
```{r}
occ <- read.csv("Data/Cuscuta_georeferenced.csv")
cc <- subset(occ, Cuscuta.Species=="C. campestris")[,1:2]
cr <- subset(occ, Cuscuta.Species=="C. reflexa")[,1:2]
ck <- subset(occ, Cuscuta.Species=="C. kilimanjari")[,1:2]
```

## *C. reflexa*
```{r}
# no African occurrences in GBIF
len.cr <- nrow(cr)

## Sample background following https://rspatial.org/raster/sdm/3_sdm_absence-background.html#
env <- raster("~/Desktop/Projects/StigaxSorghum/MacroecologyMS/env7.rs.tif")

write.table(cr, file="Data/Creflexa.occ.txt", quote=F, row.names = F, col.names = T)

coordinates(cr) <- ~Long+Lat
projection(cr) <- CRS('+proj=longlat +datum=WGS84')

# circles with a radius of 50 km
x <- circles(cr, d=300000, lonlat=TRUE)
pol <- polygons(x)

# sample randomly from all circles
samp1 <- spsample(pol, 1000, type='random', iter=25)

# get unique cells
cells <- cellFromXY(env, samp1)
cells <- unique(cells)
xy <- xyFromCell(env, cells)

map(database="world", regions=c("Kenya","Tanzania","Ethiopia","Uganda","Rwanda","Burundi","Sudan","South Sudan","Eritrea","Somalia","Malawi"))
points(xy, cex=0.75, pch=20, col='blue')
points(cr$Long, cr$Lat, col="red", pch=20)

write.table(xy, file="Data/Creflexa.bg.txt", quote=F, row.names = F, col.names = T)

```

## *C. kilimanjari*
```{r}
# combine w/GBIF data
#citation: GBIF.org (31 August 2020) GBIF Occurrence Download https://doi.org/10.15468/dl.muwe3t
gbif.ck <- read.csv("Data/C.kilimanjari_GBIF_JM.csv", header = T)
gbif.ck <- gbif.ck %>% select(Lat, Long)

ck.all <- rbind(ck, gbif.ck)
write.table(ck.all, file="Data/Ckilimanjari.occ.txt", quote=F, row.names = F, col.names = T)

len.ck <- nrow(ck.all)

## Sample background
coordinates(ck.all) <- ~Long+Lat
projection(ck.all) <- CRS('+proj=longlat +datum=WGS84')

# circles with a radius of 50 km
x <- circles(ck.all, d=300000, lonlat=TRUE)
pol <- polygons(x)

# sample randomly from all circles
samp1 <- spsample(pol, 1000, type='random', iter=25)

# get unique cells
cells <- cellFromXY(env, samp1)
cells <- unique(cells)
xy <- xyFromCell(env, cells)

map(database="world", regions=c("Kenya","Tanzania","Ethiopia","Uganda","Rwanda","Burundi","Sudan","South Sudan","Eritrea","Somalia","Malawi"))
points(xy, cex=0.75, pch=20, col='blue')
points(ck.all$Long, ck.all$Lat, col="red", pch=20)

write.table(xy, file="Data/Ckilimanjari.bg.txt", quote=F, row.names = F, col.names = T)

```

## *C. campestris*
```{r}
# combine w/GBIF data
#citation: GBIF.org (31 August 2020) GBIF Occurrence Download https://doi.org/10.15468/dl.y8rtg4
gbif.cc <- read.csv("Data/C.campestris_GBIF_JM.csv", header = T)
gbif.cc <- gbif.cc %>% select(Lat,Long)

cc.all <- rbind(cc, gbif.cc)
len.cc <- nrow(cc.all)

write.table(cc.all, file="Data/Ccampestris.occ.txt", quote=F, row.names = F, col.names = T)

## Sample background
coordinates(cc.all) <- ~Long+Lat
projection(cc.all) <- CRS('+proj=longlat +datum=WGS84')

# circles with a radius of 50 km
x <- circles(cc.all, d=300000, lonlat=TRUE)
pol <- polygons(x)

# sample randomly from all circles
samp1 <- spsample(pol, 1000, type='random', iter=25)

# get unique cells
cells <- cellFromXY(env, samp1)
cells <- unique(cells)
xy <- xyFromCell(env, cells)

map(database="world", regions=c("Kenya","Tanzania","Ethiopia","Uganda","Rwanda","Burundi","Sudan","South Sudan","Eritrea","Somalia","Malawi"))
points(xy, cex=0.75, pch=20, col='blue')
points(cc.all$Long, cc.all$Lat, col="red", pch=20)

write.table(xy, file="Data/Ccampestris.bg.txt", quote=F, row.names = F, col.names = T)
```

## Methods Summary

All occurrences for *C. reflexa* were from sampled localities (*n* = `r len.cr`). Sampled localities were combined with occurrences from GBIF for *C. campestris* (total *n* = `r len.cc`) and *C. kilimanjari* (total *n* = `r len.cc`).  Background points (*n*=1,000) were chosen from within a radius of 300 km of known occurrences.
