---
title: "Visualize ENMs"
author: "EBellis"
date: "9/2/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=F}
library(raster)
library(maps)
library(RColorBrewer)
library(spData)
library(sf)
```

## Coffee & Tea 
These are from https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/FSSKBW

Citation:
International Food Policy Research Institute, 2020, "Spatially-Disaggregated Crop Production Statistics Data in Africa South of the Saharan for 2017", https://doi.org/10.7910/DVN/FSSKBW, Harvard Dataverse, V1

Production is measured in metric tons.

# Import coffee/tea layers
```{r echo=F}
acof <- raster('~/Downloads/dataverse_files/spam2017v1r1_ssa_prod.geotiff/spam2017V1r1_SSA_gr_P_ACOF_A.tif')
rcof <- raster('~/Downloads/dataverse_files/spam2017v1r1_ssa_prod.geotiff/spam2017V1r1_SSA_gr_P_RCOF_A.tif')
cof <- acof+rcof

coff_ext <- calc(cof, fun=function(x){ x[x < 1] <- NA; return(x)})

teas <- raster('~/Downloads/dataverse_files/spam2017v1r1_ssa_prod.geotiff/spam2017V1r1_SSA_gr_P_TEAS_A.tif')
tea_ext <- calc(teas, fun=function(x){ x[x < 1] <- NA; return(x)})

```

# Create a mask for coffee/tea growing areas
```{r echo=F}
ck <- raster("Models/ck.tif")

#create a mask for coffee and tea growing areas
coff_ext <- crop(coff_ext, ck)
tea_ext <- crop(tea_ext, ck)
coff_ext2 <- resample(coff_ext, ck)
tea_ext2 <- resample(tea_ext, ck)

```

# crop/mask layers for C. kilimanjari
```{r}
library(tmap)
library(tmaptools)

sub_world <- subset(world, iso_a2=="KE"|iso_a2=="TZ"|iso_a2=="ET"|iso_a2=="UG"|iso_a2=="RW"|iso_a2=="BI")
sub_world_sp <- as(sub_world, 'Spatial')

ck.coff <- raster::mask(ck, coff_ext2)
ck.tea <- raster::mask(ck, tea_ext2)

ck.coff <- crop(ck.coff, sub_world_sp)
ck.tea <- crop(ck.tea, sub_world_sp)
ck.all <- crop(ck, sub_world_sp)

ck.coff <- raster::mask(ck.coff, sub_world_sp)
ck.tea <- raster::mask(ck.tea, sub_world_sp)
ck.all <- raster::mask(ck.all, sub_world_sp)

occ <- unique(read.table('Data/Ckilimanjari.occ.txt', header=T))
coordinates(occ)<- ~Long + Lat
projection(occ) <- CRS('+proj=longlat +datum=WGS84')

```

# plot for C. kilimanjari; no legend/inset (will be in middle row and middle column)
```{r}
sg <- bb_poly(sub_world_sp)
xy <- st_bbox(sg)
asp <- (xy$ymax - xy$ymin)/(xy$xmax - xy$xmin)

ck.tea.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(ck.tea) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.show = FALSE)

tmap_save(ck.tea.map,filename="Results/CK_Tea.pdf",
          dpi=600,height=asp*91, width=91, units="mm")

ck.coff.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(ck.coff) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.show = FALSE)

tmap_save(ck.coff.map,filename="Results/CK_Coff.pdf",
          dpi=600,height=asp*91, width=91, units="mm")

ck.all.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(ck.all) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.show = FALSE)

tmap_save(ck.all.map,filename="Results/CK_All.pdf",
          dpi=600,height=asp*91, width=91, units="mm")

```

# crop/mask layers for C. reflexa
```{r}
cr <- raster("Models/cr.tif")

cr.coff <- raster::mask(cr, coff_ext2)
cr.tea <- raster::mask(cr, tea_ext2)

cr.coff <- crop(cr.coff, sub_world_sp)
cr.tea <- crop(cr.tea, sub_world_sp)
cr.all <- crop(cr, sub_world_sp)

cr.coff <- raster::mask(cr.coff, sub_world_sp)
cr.tea <- raster::mask(cr.tea, sub_world_sp)
cr.all <- raster::mask(cr.all, sub_world_sp)

occ <- unique(read.table('Data/Creflexa.occ.txt', header=T))
coordinates(occ)<- ~Long + Lat
projection(occ) <- CRS('+proj=longlat +datum=WGS84')

```

# plot for C. reflexa; legend on tea map
```{r}
cr.tea.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(cr.tea) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.show = FALSE) + tm_scale_bar(breaks=c(0,250,500), text.size=1, position=c(0.61,'bottom'))

tmap_save(cr.tea.map,filename="Results/CR_Tea.pdf",
          dpi=600,height=asp*91, width=91, units="mm")

cr.coff.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(cr.coff) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.show = FALSE)

tmap_save(cr.coff.map,filename="Results/CR_Coff.pdf",
          dpi=600,height=asp*91, width=91, units="mm")

cr.all.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(cr.all) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.show = FALSE)

tmap_save(cr.all.map,filename="Results/CR_All.pdf",
          dpi=600,height=asp*91, width=91, units="mm")
```

## with inset 
```{r}
library(dplyr)
library(grid)

xy <- st_bbox(world %>%
  filter(continent == "Africa"))
asp2 <- (xy$xmax - xy$xmin)/(xy$ymax - xy$ymin)

#inset.map <-
africa_inset <- world %>%
  filter(continent == "Africa") %>%
  tm_shape() +
    tm_borders() + tm_fill() +
  tm_shape(sub_world_sp) +
    tm_fill(col="tomato4") + tm_borders() +
  tm_layout(inner.margins = c(0.04,0.04,0.04,0.04), outer.margins=c(0,0,0,0))

africa_inset
```

# crop/mask layers for C. campestris
```{r}
cc <- raster("Models/cc.tif")

cc.coff <- raster::mask(cc, coff_ext2)
cc.tea <- raster::mask(cc, tea_ext2)

cc.coff <- crop(cc.coff, sub_world_sp)
cc.tea <- crop(cc.tea, sub_world_sp)
cc.all <- crop(cc, sub_world_sp)

cc.coff <- raster::mask(cc.coff, sub_world_sp)
cc.tea <- raster::mask(cc.tea, sub_world_sp)
cc.all <- raster::mask(cc.all, sub_world_sp)

occ <- unique(read.table('Data/Ccampestris.occ.txt', header=T))
coordinates(occ)<- ~Long + Lat
projection(occ) <- CRS('+proj=longlat +datum=WGS84')

```

# plot for C. campestris; legend/inset for tea map
```{r}
cc.tea.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(cc.tea) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.outside=F, legend.text.size = 0.8,
            legend.title.size=0.9,
            legend.frame=TRUE, legend.position=c(0.985, 0.985),
            legend.just = c("right", "top"), legend.width=-0.25,
            legend.height=-0.4, outer.margins = c(0,0,0,0),
            inner.margins = c(0,0,0,0))

w <- 0.25
h <- asp2 * w
vp <- viewport(x=0.88, y=0.1, width = w, height=h, just=c("right", "bottom"))

tmap_save(cc.tea.map,filename="Results/CC_Tea.pdf",
          dpi=600, insets_tm=africa_inset, insets_vp=vp,
          height=asp*91, width=91, units="mm")

cc.coff.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(cc.coff) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.show = FALSE)

tmap_save(cc.coff.map,filename="Results/CC_Coff.pdf",
          dpi=600,height=asp*91, width=91, units="mm")

cc.all.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(cc.all) +
  tm_raster() + 
tm_shape(world) +
  tm_borders() +
tm_shape(occ) +
  tm_bubbles(size=0.04, alpha=0.6) +
tm_layout(legend.show = FALSE)

tmap_save(cc.all.map,filename="Results/CC_All.pdf",
          dpi=600,height=asp*91, width=91, units="mm")
```

## lim factor map for CR
```{r}
lim <- raster("Models/cr.lim.tif")
cr.lim.map <- tm_shape(sub_world_sp) +
  tm_borders() + 
tm_shape(world) +
  tm_fill() + 
tm_shape(lim) +
  tm_raster() + 
tm_shape(world) +
  tm_borders()

plot(lim
map(database="world", regions=c("Kenya","Tanzania","Ethiopia","Uganda","Rwanda","Burundi","Sudan","South Sudan","Eritrea","Somalia","Malawi"), add=T)  # 5 is bio18; 2 is bio3; 8 is tree cover
```


